Keep your Laziness in Check

### 2018-03-03 paper/main.tex
[paper] fixed accent issue

\leo{Point of first paragraph: lazy evaluation is powerful}

@@

The power of laziness puts great responsibility on programmers'
shoulders. An incorrect implementation can either behave functionally
the same but with inferior performance, or it can completely break
down! Reasoning about lazy programs is also notoriously hard --- the
programmer needs to have a mental model of the order of evaluation of
the code, and this order is not always obvious from the syntax of the
code.

@@

\leo{Insert take example here. There is enough space to have both code
and contributions in this page. yay :) }

In the next section we work through two more examples, functional
queues and functional maps, demonstrating both the difficulties of
programming with laziness and how our approach can be used to
alleviate them.
%
In the rest of the paper, we present our technical contributions:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior
of functions that is {\em precise} and {\em compositional}. Such
specifications are expressive enough to capture exactly how much
evaluation occurs within a data structure
%\leo{Also add
%drawbacks/partiality here? If not here, where in the intro?} \hzh{I'm
%not sure if we should bring in partiality (in the sense of
%divergence/nontermination) yet since that seems like a rather
%technical detail of the spec}
\item We propose a framework for testing against such specifications.
\item We improve upon the random function generators from QuickCheck to generate functions with arbitrary laziness behaviors.
\item We demonstrate non-trivial generic programming techniques to apply StrictCheck to almost all data types.
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
José Manuel Calderón Trilla,
Matt Parsons,
Stephanie Weirich,
Jennifer Paykin,
Robert Rand,
Antal Spector-Zabusky,
Matthew Weaver,
and the Penn PLClub
for their useful comments.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.

>>>>

\leo{Point of first paragraph: lazy evaluation is powerful}
\caleb{What does the word ``power'' mean? It's non-specific. Useful? Convenient?}

@@

\caleb{Again, power and responsibility are not completely clear, but I do like the narrative}
The power of laziness puts great responsibility on programmers'
shoulders. An incorrect implementation can either behave functionally
the same but with inferior \caleb{Inferior than what?} performance, or it can completely break
down!\caleb{unclear. loops?} Reasoning about lazy programs is also notoriously hard --- the
programmer needs to have a mental model of the order of evaluation of
the code, and this order is not always obvious from the syntax of the
code.

@@

\leo{Insert take example here. There is enough space to have both code
and contributions in this page. yay :) }\caleb{YES!}

In the next section we work through two more examples, functional
queues and functional maps, demonstrating both the difficulties of
programming with laziness and how our approach can be used to
alleviate them.
%
In the rest of the paper, we present our technical contributions:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior
of functions that is {\em precise} and {\em compositional}. Such
specifications are expressive enough to capture exactly how much
evaluation occurs within a data structure
%\leo{Also add
%drawbacks/partiality here? If not here, where in the intro?} \hzh{I'm
%not sure if we should bring in partiality (in the sense of
%divergence/nontermination) yet since that seems like a rather
%technical detail of the spec}
\item We propose a framework for testing against such specifications.\caleb{Automated testing? Can be more specific}
\item We improve upon the random function generators from QuickCheck\cn to generate functions with arbitrary laziness behaviors.
\item We demonstrate non-trivial generic programming techniques to apply StrictCheck to almost all data types.\caleb{I don't know
the meaning of non-trivial and almost-all}
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
We are grateful to
%
Jos\'e Manuel Calder\'on Trilla,
Matt Parsons,
Stephanie Weirich,
Jennifer Paykin,
Robert Rand,
Antal Spector-Zabusky,
Matthew Weaver,
and the Penn PLClub
for their useful comments.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
  Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{1421243} ({\em Random Testing for Language
Design}), Grant No.~\grantnum{GS100000001}{1521523} ({\em Expeditions
in Computing: The Science of Deep Specification}), and \leo{Kenny,
Hengchu, ask for grant numbers names} Any opinions, findings, and
conclusions or recommendations expressed in this material are those of
the author and do not necessarily reflect the views of the National
Science Foundation.
